---
title: "**_An Brief Introduction to R_**"
author: "*Frank Qu*"
date: "9/24/2017"
documentclass: ctexart
output:
  rticles::ctex:
    fig_caption: yes
    number_sections: yes
    toc: yes
classoption: "hyperref,"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Learning Object 

- Introduction to R and RStudio
- Reading data: importing datasets, data types, defining variable
classes
- Manipulating data: cleaning, manipulate, package dplyr
- Analyzing data: statistical properties, regression model, limited
dependent variables
- Visualizing data: built-in plotting functions and ggplot2 package

# Getting Stared With R 

- Not only a statistical programming language, but a computing environment for statistical computing and graphics.
- Powerful Programming and Extending Capability 
- Multiple Platforms
- Very excellent graphics 
- A big but not a determinate advantage:
  FREE 
  Open Source
  
## Installing 

### Installing R (skip)
 
### Using IDE: RStudio (skip) 
  
- The most popular IDE for R 
- Also Free(for basic version)
- Combine with \texttt{Markdown} and  \texttt{Latex} to make scientific writings or presentation easier
- Download it from here: [RStudio]{https://www.rstudio.com/products/rstudio/download/}

## Using R as \texttt{Stata}: Packages

- Many researchers provide their own R programs through the R project webpage. 
- Many packages are already preinstalled in the basic R installation.
- They can be directly activated from RStudio.
- Or they are activated by issuing a command in the Console.

```{r install, echo=TRUE}
#install.packages("AER",repos = "http://mirrors.xmu.edu.cn/CRAN/")
#library("AER")
#install.packages("haven",repos = "http://mirrors.xmu.edu.cn/CRAN/")
```

## Where to get help

- The online help in R describes all basic R commands as well as commands in active packages. 
- search the online help from the Help pane in RStudio.
- Alternatively, using the command

```{r help, echo=TRUE}
?load
# or
help("load")
# or
??load
# or
help.search("read")
```


# Basic Data Management in R

## Working Directory
- R will look for data or save data in the drive and working directory.
- The working directory is specified depending on the operation system
```{r, echo=TRUE}
getwd()
```

## Changing the Working Directory

```{r,echo=TRUE}
setwd("/Users/byelenin/Dropbox/R/R_Class/Metrics/Lec1/")
getwd()
```

##  Importing Data: From STATA

- R will look for data or save data in the drive and working directory.
- The working directory is specified depending on the operation system
- imports data from STATA

```{r stata13, echo=TRUE}
#install.packages("haven",repos = "http://mirrors.xmu.edu.cn/CRAN/")
library(haven)
caschool_data <- read_dta("/Users/byelenin/Dropbox/R/R_Class/Metrics/Lec1/caschool.dta")
View(caschool_data)
```

##  Importing Data: From CSV
```{r csv, echo=TRUE,message=TRUE}
caschool_csv <- read.csv("/Users/byelenin/Dropbox/R/R_Class/Metrics/Lec1/caschool.csv")
View(caschool_csv) 
```
## Summary the Data
```{r school_summary, echo = TRUE}
summary(caschool_data)
```

## Variables

```{r dplyr, include=FALSE}
#install.packages("dplyr")
library(dplyr)

```
```{r name, echo=TRUE}
#install.packages("dplyr")
names(caschool_data)
```
### Keeping Variables

```{r small, echo=TRUE}
caschool_data_small <- select(caschool_data,observat,testscr,str,expn_stu,el_pct)
head(caschool_data_small)

```

###  Generate new variable
```{r data, echo=TRUE}

caschool_data_small$logexp <- log(caschool_data$expn_stu)

caschool_data_small$el_high <- caschool_data$el_pct>=50


head(caschool_data_small)
```

## Descriptive Statistics

- summary a variable
```{r summary, echo=TRUE}
summary(caschool_data_small$testscr)
```
- if the dataframe is attached, simply

```{r sum2, echo=TRUE}
attach(caschool_data_small)
summary(testscr)
```

# Plot

## Scatter Plot
- Draw a scatter plot of the variable "testscr" against "str":
```{r scatt, echo=TRUE}
plot(str, testscr)
abline(lm(testscr ~ str , data = caschool_data_small),col = "red")
```
- ggplot2 
```{r ggplot2, echo=TRUE}
library("ggplot2")
ggplot(data =caschool_data_small,aes(x=str, y=testscr)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm)   # Add linear regression line 
                             #  (by default includes 95% confidence region)
```

## A kdensity distribution of income

```{r density, echo=TRUE}
caschool_data$inc <- with(caschool_data,avginc >=15)
ggplot(caschool_data,aes(x=avginc))+
  geom_density(fill="grey",color ="blue")+
  geom_vline(xintercept = 15)

caschool_data$logavginc <- log(caschool_data$avginc)
ggplot(caschool_data,aes(x=logavginc))+
  geom_density(fill="grey",color ="blue")

```

# T-test in R 

## single sample

- t-test for scores

```{r s1-test,echo=TRUE}
summary(caschool_data_small$testscr)
t.test(caschool_data_small$testscr,alternative = "two.sided",mu = 650) 

```

- Construct t-Statistics

```{r s2-test,echo=TRUE}
randT <- rt(30000,df=NROW(testscr)-1) # build a distribution
scoreTtest <- t.test(caschool_data_small$testscr,alternative = "two.sided",mu = 650) 
ggplot(data.frame(x=randT)) +
         geom_density(aes(x=x),fill = "grey",color ="blue") +
         geom_vline(xintercept = scoreTtest$statistic) +
         geom_vline(xintercept = mean(randT) + c(-2,2)*sd(randT),linetype = 2)
```

## T-test for the difference between two means

```{r s3-test,echo=TRUE}
t.test(testscr~el_high,data = caschool_data_small) 

```


# Rstudio for run commands and processing markdown files

## R script similar to Stata dofile
- A script is a text file with a set of R commands that can be executed jointly.
- Script files are convenient because they automate tasks relative to type each command in the Console
- Open a R script from the top-left corner or File, New File, R Script etc.

## Rmarkdown documents

- generate a new Rmarkdown


# Online Resource

## R tutorial 

- Datacamp 
- Big Data University

## Markdown 


## Latex 



